Quantum Hoare Types

### 2019-10-30 paper/paper.tex
More cleanup, remove template which is usually packaged

%% For double-blind review submission, w/o CCS and ACM Reference (max submission space)
%\documentclass[acmsmall,review,anonymous]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For double-blind review submission, w/ CCS and ACM Reference
%\documentclass[acmsmall,review,anonymous]{acmart}\settopmatter{printfolios=true}
%% For single-blind review submission, w/o CCS and ACM Reference (max submission space)
\documentclass[acmsmall,nonacm]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For single-blind review submission, w/ CCS and ACM Reference
%\documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true}
%% For final camera-ready submission, w/ required CCS and ACM Reference
%\documentclass[acmsmall]{acmart}\settopmatter{}

%% Journal information
%% Supplied to authors by publisher for camera-ready submission;
%% use defaults for review submission.
\acmJournal{PACMPL}
\acmVolume{1}
\acmNumber{CONF} % CONF = POPL or ICFP or OOPSLA
\acmArticle{}
\acmYear{2018}
\acmMonth{1}
\acmDOI{} % \acmDOI{10.1145/nnnnnnn.nnnnnnn}
\startPage{1}

%% Copyright information
%% Supplied to authors (based on authors' rights management selection;
%% see authors.acm.org) by publisher for camera-ready submission;
%% use 'none' for review submission.
\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\copyrightyear{2018}           %% If different from \acmYear

%% Bibliography style
\bibliographystyle{ACM-Reference-Format}
%% Citation style
%% Note: author/year citations are required for papers published as an
%% issue of PACMPL.
\citestyle{acmauthoryear}   %% For author/year citations

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Note: Authors migrating a paper from PACMPL format to traditional
%% SIGPLAN proceedings format must update the '\documentclass' and
%% topmatter commands above; see 'acmart-sigplanproc-template.tex'.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% Some recommended packages.
\usepackage{booktabs}   %% For formal tables:
                        %% http://ctan.org/pkg/booktabs
\usepackage{subcaption} %% For complex figures with subfigures/subcaptions
                        %% http://ctan.org/pkg/subcaption

%% Added by kartik
\usepackage[braket]{qcircuit}
\usepackage{mathpartir}
\usepackage{xspace}

@@

%% Title information
\title[Quantum Hoare Types]{Quantum Hoare Types}         %% [Short Title] is optional;
                                        %% when present, will be used in
                                        %% header instead of Full Title.
%\titlenote{with title note}             %% \titlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'
%\subtitle{Subtitle}                     %% \subtitle is optional
%\subtitlenote{with subtitle note}       %% \subtitlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'

%% Author information
%% Contents and number of authors suppressed with 'anonymous'.
%% Each author should be introduced by \author, followed by
%% \authornote (optional), \orcid (optional), \affiliation, and
%% \email.
%% An author may have multiple affiliations and/or emails; repeat the
%% appropriate command.
%% Many elements are not rendered, but should be provided for metadata
%% extraction tools.

%% Author with single affiliation.
\author{Kartik Singhal}
%\authornote{with author1 note}          %% \authornote is optional;
                                        %% can be repeated if necessary
\orcid{0000-0003-1132-269X}             %% \orcid is optional
\affiliation{
%  \position{Position1}
  \department{Department of Computer Science}              %% \department is recommended
  \institution{University of Chicago}            %% \institution is required
%  \streetaddress{Street1 Address1}
%  \city{City1}
%  \state{State1}
%  \postcode{Post-Code1}
  \country{USA}                    %% \country is recommended
}
\email{ks@cs.uchicago.edu}          %% \email is recommended

%% Author with two affiliations and emails.
%\author{John Reppy}
%\authornote{with author2 note}          %% \authornote is optional;
                                        %% can be repeated if necessary
%\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
%\affiliation{
%%  \position{Position2a}
%  \department{Department of Computer Science}             %% \department is recommended
%  \institution{University of Chicago}           %% \institution is required
%%  \streetaddress{Street2a Address2a}
%%  \city{City2a}
%%  \state{State2a}
%%  \postcode{Post-Code2a}
%  \country{United States}                   %% \country is recommended
%}
%\email{jhr@cs.uchicago.edu}         %% \email is recommended
%\affiliation{
%  \position{Position2b}
%  \department{Department2b}             %% \department is recommended
%  \institution{Institution2b}           %% \institution is required
%  \streetaddress{Street3b Address2b}
%  \city{City2b}
%  \state{State2b}
%  \postcode{Post-Code2b}
%  \country{Country2b}                   %% \country is recommended
%}
%\email{first2.last2@inst2b.org}         %% \email is recommended

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
(4 sentences)

@@

%% 2012 ACM Computing Classification System (CSS) concepts
%% Generate at 'http://dl.acm.org/ccs/ccs.cfm'.
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10011007.10011006.10011008</concept_id>
<concept_desc>Software and its engineering~General programming languages</concept_desc>
<concept_significance>500</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Software and its engineering~General programming languages}
%% End of generated code

%% Keywords
%% comma separated list
\keywords{keyword1, keyword2, keyword3}  %% \keywords are mandatory in final camera-ready submission

%% \maketitle
%% Note: \maketitle command must come after title commands, author
%% commands, abstract environment, Computing Classification System
%% environment and commands, and keywords command.
\maketitle

\section{Introduction}
(1 page)

\textit{- Describe the problem}

\textit{- State your contributions}

@@

\subsection{Contributions}
(bulleted list of contributions)

\textit{In this section we present the main contributions of the paper\ldots}

\section{Problem}
(1 page)

\textit{Use an example to introduce the problem}

@@

\section{Idea}
(2 pages)

\textit{The main idea of this paper is \ldots}

@@

\section{Details}
(5 pages)

@@

\section{Related Work}
(1-2 pages)

\cite{huang2018}

\cite{huang2019}

\cite{nanevski2008}

\cite{paykin2018}

\cite{rand2018a}

\cite{ross2015algebraic}

\cite{ringer2019}

\cite{silq}

@@

(0.5 page)

%% Acknowledgments
\begin{acks}                            %% acks environment is optional
                                        %% contents suppressed with 'anonymous'
  %% Commands \grantsponsor{<sponsorID>}{<name>}{<url>} and
  %% \grantnum[<url>]{<sponsorID>}{<number>} should be used to
  %% acknowledge financial support and will be used by metadata
  %% extraction tools.
  This material is based upon work supported by
  EPiQC, an \grantsponsor{GS100000001}{NSF}{http://dx.doi.org/10.13039/100000001}
  Expedition in Computing, under Grant
  No.~\grantnum{GS100000001}{1730449}.  Any opinions, findings, and
  conclusions or recommendations expressed in this material are those
  of the authors and do not necessarily reflect the views of the
  National Science Foundation.
\end{acks}

%% Bibliography
\bibliography{bibfile}

%% Appendix
\appendix
\section{Appendix}

Text of appendix \ldots

>>>>

\documentclass[acmsmall,nonacm]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}

\acmJournal{PACMPL}
\acmVolume{}
\acmNumber{} %
\acmArticle{}
\acmYear{}
\acmMonth{}
\acmDOI{} %
\startPage{1}

\setcopyright{none}

\bibliographystyle{ACM-Reference-Format}
\citestyle{acmauthoryear}   %

\usepackage{booktabs}   %
\usepackage{subcaption} %

\usepackage[braket]{qcircuit}
\usepackage{mathpartir}
\usepackage{xspace}

@@

\title[Quantum Hoare Types]{Quantum Hoare Types}         %

\author{Kartik Singhal}
\orcid{0000-0003-1132-269X}             %
\affiliation{
  \department{Department of Computer Science}              %
  \institution{University of Chicago}            %
  \country{USA}                    %
}
\email{ks@cs.uchicago.edu}          %

@@

\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10011007.10011006.10011008</concept_id>
<concept_desc>Software and its engineering~General programming languages</concept_desc>
<concept_significance>500</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Software and its engineering~General programming languages}

\keywords{Quantum Computing, Programming Languages, Type Systems, Dependent Types}  %

\maketitle

\section{Introduction}
%(1 page)
%
%\textit{- Describe the problem}
%
%\textit{- State your contributions}

@@

%\subsection{Contributions}
%(bulleted list of contributions)
%
%\textit{In this section we present the main contributions of the paper\ldots}

\section{Problem}
%(1 page)
%
%\textit{Use an example to introduce the problem}

@@

\section{Idea}
%(2 pages)
%
%\textit{The main idea of this paper is \ldots}

@@

\section{Details}
%(5 pages)

@@

\section{Related Work}
%(1-2 pages)

@@

%(0.5 page)

\begin{acks}                            %
  This material is based upon work supported by
  EPiQC, an \grantsponsor{GS100000001}{NSF}{http://dx.doi.org/10.13039/100000001}
  Expedition in Computing, under Grant
  No.~\grantnum{GS100000001}{1730449}.  Any opinions, findings, and
  conclusions or recommendations expressed in this material are those
  of the authors and do not necessarily reflect the views of the
  National Science Foundation.
\end{acks}

\bibliography{bibfile}

%\appendix
%\section{Appendix}

%Text of appendix \ldots
